Achieving maximum possible precision on stellar radial-velocity measurements in multi-epoch spectroscopy

### 2017-12-04 paper/paper.tex
tweak first sentences

Accurate spectroscopic measurements of radial velocities (\RV s) have long been a critical tool across many subfields of astronomy, from galactic dynamics to cosmic expansion. In recent decades, however, a new focus has emerged on \textit{extremely precise} \RV\ measurements of stars as a means of detecting exoplanets. For this application, measuring the absolute velocity of the star is much less important than resolving its changes through time. With sub-$\ms$-level precision required for the detection of Earth-like planets, vast amounts of effort have been poured into the engineering challenges of constructing a sufficiently stable spectrograph (or, failing that, being able to track the drift of a spectrograph over time) \todo{(cite some review papers)}. At the same time, great strides have been made towards disentangling true Doppler shifts from imitative signals like the spectral signatures of stellar pulsations and magnetic activity features \todo{(cite some review papers)}.  In this work, we investigate another fundamentally important but less commonly discussed aspect of the quest for maximum-precision \RV s: the method of analysis used to extract the \RV\ from a stellar spectrum.

>>>>

Accurate spectroscopic measurements of radial velocities (\RV s) have long been a critical tool across many subfields of astronomy, from Galactic dynamics to large-scale structure and cosmic expansion.
Fundamentally, accuracy of radial-velocity mesurement is limited by the quality of spectral models of stars, or templates.
In recent decades, however, a new focus has emerged on \emph{extremely precise} but purely \emph{relative} \RV\ measurements of stars as a means of detecting exoplanets and other kinds of companions.
For this application, measuring the absolute velocity of the star is much less important than resolving changes through time.
With sub-$\ms$-level precision required for the detection of Earth-like planets, vast amounts of effort have been poured into the engineering challenges of constructing a sufficiently stable spectrograph (or, failing that, being able to track the drift of a spectrograph over time) \todo{(cite some review papers)}. At the same time, great strides have been made towards disentangling true Doppler shifts from imitative signals like the spectral signatures of stellar pulsations and magnetic activity features \todo{(cite some review papers)}.  In this work, we investigate another fundamentally important but less commonly discussed aspect of the quest for maximum-precision \RV s: the method of analysis used to extract the \RV\ from a stellar spectrum.
